---
output:
  pdf_document: default
  html_document: default
---
concatenate raw data, call python function to organize columns
```{bash}
STUDY_DIR=/Volumes/crisp/hinl/bandit/gems_vs_bomb
STUDY=b6
STANDARDIZE_PY=/Users/wem3/Developer/zach/csv_ops/standardize_columns.py 
RAW_DIR=${STUDY_DIR}/raw/${STUDY}
TMP_FILE=/tmp/tmp.csv
python $STANDARDIZE_PY -i $RAW_DIR -o $TMP_FILE
```

import data table from tmp.csv
```{r}
library("data.table")
dt <- fread("/tmp/tmp.csv")
dt[trial_type == "button-response", button_pressed]
```
Convert subjID to string if desired to left pad with 0s
```{r}
#dt[,subjID:=leftPadFunction(as.character(subjID))]
```
We only want people who are Dem or Rep
```{r}
partisans <- dt[trial_type == "button-response" & button_pressed %in% c(0, 1), .(subjID, button_pressed)]
```
Set party--0 == Republican, 1 == Democrat
```{r}
partisans[, party := ifelse(button_pressed == 0, "Republican", "Democrat")]
```
Filter full dset to only have Dem/Rep & merge in party info
```{r}
dt <- dt[subjID %in% partisans$subjID]
dt <- partisans[dt, on="subjID"]
```
parse dt for trial data
```{r}
setkey(dt,"subjID","trial_counter")
trial_data <- dt[trial_label=="main_expt", .(subjID,trial_counter,respChoiceNum,gems,bombs,rt)]
probs <- unique(dt[trial_label=="main_expt", .(subjID,GainOverPainPr_0, GainOverPainPr_1, GainOverPainPr_2, GainOverPainPr_3)])
```
```{r}
CLEAN_DIR <- "/Volumes/crisp/hinl/bandit/gems_vs_bomb/clean/"
write.csv(trial_data,file = paste0(CLEAN_DIR,"b6_trial_data_R.csv"),row.names=FALSE)
```
Get demographics and merge with political party
```{r}
demo <- dt[trial_type=="survey-text-sam", .(subjID, age, gender, ethnicity)]
demo <- partisans[demo, on = "subjID"]
demo <- probs[demo, on = "subjID"]
```
Get identification scores
```{r}
identification <- dt[trial_type == "identification"]
identification[party == "Democrat", target_relative := ifelse(target == "the Democratic Party", "ingroup", "outgroup")]
identification[party == "Republican", target_relative := ifelse(target == "the Republican party", "ingroup", "outgroup")]
identification <- identification[ , .(ident_score = (like + value + connected)/ 3), .(subjID, expt_phase, target_relative)]
identification
```
Reshape so each subj is on one line
```{r}
identification <- dcast(identification, subjID ~ expt_phase + target_relative, value.var = "ident_score")
identification
```
Join that into the demographic info
```{r}
demo <- identification[demo, on = "subjID"]
write.csv(x = demo, file = paste0(CLEAN_DIR, "b6_demo.csv"))
demo
```